---
title: "Distributions (normal, binomial, poisson…)"
output: pdf_document
author: Ingrid Brizotti
---

The goal is to show how to create different distributions and help those are new on R.
\hspace*{1cm}

Distribution  | Random number |  PDF    |  CDF    | Quantile 
------------  --------------  --------- --------  ----------------
Normal        | rnorm         | dnorm   | pnorm   | qnorm
Binomial      | rbinom        | dbinom  | pbinom  | qbinom  
Poisson       | rpois         | dpois   | ppois   | qpois  
t             | rt            | dt      | pt      | qt 
F             | rf            | df      | pf      | qf 
Chi-Squared   | rchisq        | dchisq  | pchisq  | qchisq
Gamma         | rgamma        | dgamma  | pgamma  | qgamma
Geometric     | rgeom         | dgeom   | pgeom   | qgeom 
Exponential   | rexp          | dexp    | pexp    | qexp 
Weibull       | rweibull      | dweibull|pweibull | qweibull 
Uniform       | runif         | dunif   | punif   | qunif 
Beta          | rbeta         | dbeta   | pbeta   | qbeta 
Multinomial   | rmultinom     |dmultinom|pmultinom| qmultinom 
Hypergeometric| rhyper        | dhyper  | phyper  | qhyper
Log-normal    | rlnorm        | dlnorm  | plnorm  | qlnorm
Logistic      | rlogis        | dlogis  | plogis  | qlogis



Where PDF means Probability Density Function, and CDF is Cumulative Density Function.

\hspace*{1cm}

**Normal (or Gaussian)**
```{r}
# generate 10 standard normal random numbers
rnorm(10)

# generate 1000 random numbers (has mean 0 and standard deviation 1)
a <- rnorm(1000)
hist(a, main ="Gaussian distribution")

# Defining mean and standard deviation
dist_normal <- rnorm(120, mean=50, sd=5)
hist(dist_normal, main ="Gaussian distribution of mean 50 and sd 5")

# checking the mean and standard deviation
mean(dist_normal)
sd(dist_normal)

# Finding a proportion (less than 2) 
sum(a < 2)/1000

# or using Cumulative Density Function (CDF) --> gives the area under curve 
pnorm(2)

# Probability Density Function (PDF) --> gives the density (height of the PDF) of the normal with mean=1 and sd=.5. 
densities <- dnorm(0, 1, .5)

# Quantile Function (inverse of pnorm) --> gives the value at which the CDF of the standard normal is .65
qnorm(0.65, 0, 1)

```

\hspace*{1cm}

**Binomial**
```{r}
# Generate 10 binomial random numbers with parameters n = 5 and p =0.7:
rbinom(10, 5, .7)

# To simulate the number of successes out of 6 trials with probability 0.4 of success, 
# we run rbinom with n=1, size=6 (trial size), and prob=0.4
rbinom(1, size=6, prob=0.4)

# probability of 2 successes out of 10
dbinom(x=2, size=10, prob=0.2)

# probability of 2 or fewer successes out of 10
pbinom(q=2, size=10, prob=0.2)
```


\hspace*{1cm}

**Poisson**
```{r}
# Generate 20.000 Poisson random numbers with lambda = 4:
dist_poisson <- rpois(20000, 4)
hist(dist_poisson, main="Poisson distribution")

# Estimate the mean and variance of a Poisson random variable whose mean
# is 8.2 by simulating 1.000 Poisson random numbers.
vpoi <- rpois(1000,8.2)

# check the mean and variance
mean(vpoi)
var(vpoi)
```





